\documentclass[a4paper,man,natbib]{apa6}
%DIF LATEXDIFF DIFFERENCE FILE
%DIF DEL paper.tex       Thu Dec 10 17:38:58 2015
%DIF ADD paper_rev.tex   Thu Dec 10 23:03:20 2015

\usepackage{apacite}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

%DIF 10d10
%DIF < \title{A Review of the Movie \textit{Apocalypse Now}}
%DIF -------
\shorttitle{A Review of the Movie \textit{Apocalypse Now}}
%DIF 12a11-12
 %DIF > 
\title{A Review of the Movie \textit{Apocalypse Now}} %DIF > 
%DIF -------
\author{Samuel Pilla}
\affiliation{Missouri University of Science and Technology}

%DIF < \abstract{\textit{Apocalypse Now} is a film directed by Francis Frank Coppola. It follows the main character, Captain Benjamin L. Willard, through his last mission in Vietnam. Assigned with assassinating the rogue Captain Walter E. Kurtz, he accompanies four other crew members, Chief, Chef, Clean, and Lance, through the chaos of the Vietnam War. The film dives into the dark progression of these characters and how the mission Willard is desperate to finish affects them and those they encounter, friend or foe. This paper will explore the applications of Abnormal Psychology in the film, including correct and incorrect aspects of symptoms, diagnosis, and other disorders that are depicted in the movie. Using the DSM-V as the source for determining the accuracy of disorders, Willard, Chef, and Lance will be examined to outline which disorder, or disorders, they exhibit and which the film may inaccurately depict. Because the film is based in the Vietnam War, the perspective when analyzing the characters will be shifted to fit the setting, potentially causing a diagnosis to be different than the diagnosis of a “normal” life experience.}
%DIF -------
\abstract{\textit{Apocalypse Now} is a film directed by Francis Frank Coppola. It follows the main character, Captain Benjamin L. Willard, through his last mission in Vietnam. Assigned with assassinating the rogue Captain Walter E. Kurtz, he is accompanied by four other crew members, Chief, Chef, Clean, and Lance, through the chaos of the Vietnam War. The film dives into the dark progression of these characters and how the mission Willard was desperate to finish affected them and those they encountered, friend or foe. This paper will explore the applications of Abnormal Psychology in the film, including correct and incorrect aspects of symptoms, diagnosis, and other disorders that are depicted in the film. Using the DSM-V as the source for determining the accuracy of disorders, Willard, Chef, and Lance will be examined to outline which disorder, or disorders, they exhibit and which the film may inaccurately depict. Because the film is based in the Vietnam War, the perspective when analyzing the characters will be shifted to fit the setting, potentially causing a diagnosis to be different than the diagnosis of a civilian life experience.} %DIF > 
%DIF PREAMBLE EXTENSION ADDED BY LATEXDIFF
%DIF UNDERLINE PREAMBLE %DIF PREAMBLE
\RequirePackage[normalem]{ulem} %DIF PREAMBLE
\RequirePackage{color}\definecolor{RED}{rgb}{1,0,0}\definecolor{BLUE}{rgb}{0,0,1} %DIF PREAMBLE
\providecommand{\DIFadd}[1]{{\protect\color{blue}\uwave{#1}}} %DIF PREAMBLE
\providecommand{\DIFdel}[1]{{\protect\color{red}\sout{#1}}}                      %DIF PREAMBLE
%DIF SAFE PREAMBLE %DIF PREAMBLE
\providecommand{\DIFaddbegin}{} %DIF PREAMBLE
\providecommand{\DIFaddend}{} %DIF PREAMBLE
\providecommand{\DIFdelbegin}{} %DIF PREAMBLE
\providecommand{\DIFdelend}{} %DIF PREAMBLE
%DIF FLOATSAFE PREAMBLE %DIF PREAMBLE
\providecommand{\DIFaddFL}[1]{\DIFadd{#1}} %DIF PREAMBLE
\providecommand{\DIFdelFL}[1]{\DIFdel{#1}} %DIF PREAMBLE
\providecommand{\DIFaddbeginFL}{} %DIF PREAMBLE
\providecommand{\DIFaddendFL}{} %DIF PREAMBLE
\providecommand{\DIFdelbeginFL}{} %DIF PREAMBLE
\providecommand{\DIFdelendFL}{} %DIF PREAMBLE
%DIF END PREAMBLE EXTENSION ADDED BY LATEXDIFF

\begin{document}
\maketitle

\DIFdelbegin \section{\DIFdel{Introduction}}
%DIFAUXCMD
\addtocounter{section}{-1}%DIFAUXCMD
%DIFDELCMD < 

%DIFDELCMD < %%%
\DIFdelend \textit{Apocalypse Now} focuses on Captain Benjamin L. Willard and his last mission during the Vietnam War. The film opens with Willard experiencing images and sounds of the war, hearing the fan \DIFdelbegin \DIFdel{as a chopper}\DIFdelend \DIFaddbegin \DIFadd{of a chopper, }\DIFaddend and watching tree lines be incinerated by air strikes. When he finally \DIFdelbegin \DIFdel{snaps }\DIFdelend \DIFaddbegin \DIFadd{snapped }\DIFaddend out of his trance, he \DIFdelbegin \DIFdel{realizes }\DIFdelend \DIFaddbegin \DIFadd{realized }\DIFaddend he is not in the jungle, where he \DIFdelbegin \DIFdel{longs }\DIFdelend \DIFaddbegin \DIFadd{longed }\DIFaddend to be, but rather in a Saigon hotel. He \DIFdelbegin \DIFdel{describes }\DIFdelend \DIFaddbegin \DIFadd{described }\DIFaddend his life back home after the first tour as boring, dull, and undesirable. He had divorced his wife, and only wanted to be back in action. While in the hotel room, he slowly \DIFdelbegin \DIFdel{falls }\DIFdelend \DIFaddbegin \DIFadd{fell }\DIFaddend into madness. Drinking, smoking, wild dancing, punching glass, and other self-inflicted wounds finally \DIFdelbegin \DIFdel{lead }\DIFdelend \DIFaddbegin \DIFadd{led }\DIFaddend up to him being called upon for a very particular mission, one he \DIFdelbegin \DIFdel{describes }\DIFdelend \DIFaddbegin \DIFadd{described }\DIFaddend as "the last he will ever need" \DIFaddbegin \DIFadd{(Coppola, 1979)}\DIFaddend .

After being assisted in getting cleaned up and presentable, Willard \DIFdelbegin \DIFdel{meets }\DIFdelend \DIFaddbegin \DIFadd{met }\DIFaddend with his superior officers. He \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{wad }\DIFaddend then assigned the mission: assassinate the rogue Colonel Kurtz, who \DIFdelbegin \DIFdel{has }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend gone to Cambodia and built his own empire. Kurtz \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend being praised as a god, and \DIFdelbegin \DIFdel{leading }\DIFdelend \DIFaddbegin \DIFadd{led }\DIFaddend with ruthless authority. \DIFdelbegin \DIFdel{Being described }\DIFdelend \DIFaddbegin \DIFadd{Described }\DIFaddend as insane and off the rails, Willard is encouraged to kill with extreme prejudice.

As Willard \DIFdelbegin \DIFdel{begins }\DIFdelend \DIFaddbegin \DIFadd{began }\DIFaddend his journey towards Kurtz, he \DIFdelbegin \DIFdel{reflects }\DIFdelend \DIFaddbegin \DIFadd{reflected }\DIFaddend on his own actions, on how many "Charlies", or Vietcong, he \DIFdelbegin \DIFdel{has }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend killed, and \DIFdelbegin \DIFdel{begins }\DIFdelend \DIFaddbegin \DIFadd{began }\DIFaddend to wonder what happened to Kurtz \DIFaddbegin \DIFadd{(Coppola, 1979)}\DIFaddend . What about the war really made him snap and go rogue?

He \DIFdelbegin \DIFdel{meets }\DIFdelend \DIFaddbegin \DIFadd{met }\DIFaddend up with the Navy crew known as the PBR, consisting of the captain Chief, and three others, Chef, Clean, and Lance. They are assigned to take Willard where he needs to go. However, the mission \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend top secret, \DIFdelbegin \DIFdel{so the crew is }\DIFdelend \DIFaddbegin \DIFadd{which made the crew }\DIFaddend very hesitant. Willard \DIFdelbegin \DIFdel{informs }\DIFdelend \DIFaddbegin \DIFadd{informed }\DIFaddend them that the only way to reach the destination \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend through the Nung River, which Chief \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend somewhat reluctant to go on. The entrances \DIFdelbegin \DIFdel{are }\DIFdelend \DIFaddbegin \DIFadd{were }\DIFaddend not always deep enough for the boat, and \DIFdelbegin \DIFdel{are }\DIFdelend \DIFaddbegin \DIFadd{were }\DIFaddend typically crawling with enemies. However, the crew \DIFdelbegin \DIFdel{begins }\DIFdelend \DIFaddbegin \DIFadd{began }\DIFaddend to boat towards the Nung River, \DIFdelbegin \DIFdel{light-hearted and expected nothing but the expected}\DIFdelend \DIFaddbegin \DIFadd{filled with light hearts}\DIFaddend .

Before reaching the river, they \DIFdelbegin \DIFdel{rendezvous }\DIFdelend \DIFaddbegin \DIFadd{rendezvoused }\DIFaddend with Lieutenant Colonel Bill Kilgore, who \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend in charge of a helicopter air squadron. They \DIFdelbegin \DIFdel{discuss }\DIFdelend \DIFaddbegin \DIFadd{discussed }\DIFaddend getting to the Nung River, and are met with great resistance until Kilgore \DIFdelbegin \DIFdel{discovers Lance is }\DIFdelend \DIFaddbegin \DIFadd{discovered Lance was }\DIFaddend a professional surfer. \DIFdelbegin \DIFdel{Being a }\DIFdelend \DIFaddbegin \DIFadd{A }\DIFaddend surfing fan himself, and being informed one of the main entrances to the Nung River \DIFdelbegin \DIFdel{has }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend six foot waves, he \DIFdelbegin \DIFdel{agrees }\DIFdelend \DIFaddbegin \DIFadd{agreed }\DIFaddend to assist. When \DIFdelbegin \DIFdel{arriving }\DIFdelend \DIFaddbegin \DIFadd{they arrived }\DIFaddend at the mouth of the river, Kilgore \DIFdelbegin \DIFdel{shows }\DIFdelend \DIFaddbegin \DIFadd{showed }\DIFaddend his true colors, blasting "Ride of the Valkyries" while raining death onto the village below. After decimating the village, Kilgore \DIFdelbegin \DIFdel{demands }\DIFdelend \DIFaddbegin \DIFadd{demanded }\DIFaddend two of his men test the waters for surfing, while mortars \DIFdelbegin \DIFdel{are bombarding }\DIFdelend \DIFaddbegin \DIFadd{bombarded }\DIFaddend around them from the edges of the jungle\DIFdelbegin \DIFdel{around the village}\DIFdelend . Eventually, a napalm strike on the tree line \DIFdelbegin \DIFdel{ends }\DIFdelend \DIFaddbegin \DIFadd{ended }\DIFaddend most of the fighting, but \DIFdelbegin \DIFdel{begins }\DIFdelend \DIFaddbegin \DIFadd{began }\DIFaddend to end the good surf. Kilgore \DIFdelbegin \DIFdel{pleads }\DIFdelend \DIFaddbegin \DIFadd{pleaded }\DIFaddend with Lance to stick around instead of continuing up the Nung River, but Willard craftily \DIFdelbegin \DIFdel{gets }\DIFdelend \DIFaddbegin \DIFadd{got }\DIFaddend the PBR crew out, and even \DIFdelbegin \DIFdel{manages }\DIFdelend \DIFaddbegin \DIFadd{managed }\DIFaddend to steal Kilgore's favorite surf board.

While hiding out from Kilgore's search parties under the low overhang of trees, Chef and Willard \DIFdelbegin \DIFdel{decide }\DIFdelend \DIFaddbegin \DIFadd{decided }\DIFaddend to wander into the jungle in search of mangoes. After a short walk and discussing the origin of Chef's name, Willard \DIFdelbegin \DIFdel{hears rustling and becomes }\DIFdelend \DIFaddbegin \DIFadd{heard rustling and became }\DIFaddend extremely alert. He \DIFdelbegin \DIFdel{pulls }\DIFdelend \DIFaddbegin \DIFadd{pulled }\DIFaddend back some large brush, only to reveal a tiger, which \DIFdelbegin \DIFdel{attacks}\DIFdelend \DIFaddbegin \DIFadd{attacked}\DIFaddend . The two \DIFdelbegin \DIFdel{scramble }\DIFdelend \DIFaddbegin \DIFadd{scrambled }\DIFaddend back to the boat, screaming hysterically and forcing Clean to unload the machine gun. When they finally get back on the boat and \DIFdelbegin \DIFdel{explain }\DIFdelend \DIFaddbegin \DIFadd{explained }\DIFaddend what happened, Chef \DIFdelbegin \DIFdel{starts }\DIFdelend \DIFaddbegin \DIFadd{started }\DIFaddend to curse and swear that he is done with the war, demanding to leave. However, he \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend calmed down while Chief \DIFdelbegin \DIFdel{starts }\DIFdelend \DIFaddbegin \DIFadd{started }\DIFaddend the boat and \DIFdelbegin \DIFdel{continues }\DIFdelend \DIFaddbegin \DIFadd{continued }\DIFaddend on. 

Eventually the crew \DIFdelbegin \DIFdel{reaches }\DIFdelend \DIFaddbegin \DIFadd{reached }\DIFaddend Hau Phat, a resupply camp they desperately \DIFdelbegin \DIFdel{need}\DIFdelend \DIFaddbegin \DIFadd{needed}\DIFaddend . After being brushed off when asking for more fuel, Willard \DIFdelbegin \DIFdel{takes }\DIFdelend \DIFaddbegin \DIFadd{took }\DIFaddend actions into his own hands. He \DIFdelbegin \DIFdel{grabs }\DIFdelend \DIFaddbegin \DIFadd{grabbed }\DIFaddend the soldier in charge of distributing supplies and \DIFdelbegin \DIFdel{demands }\DIFdelend \DIFaddbegin \DIFadd{demanded }\DIFaddend fuel. The soldier \DIFdelbegin \DIFdel{agrees and apologizes}\DIFdelend \DIFaddbegin \DIFadd{agreed and apologized}\DIFaddend , also giving the crew free tickets to the Playboy bunnies' show.

The crew is gathered \DIFdelbegin \DIFdel{in }\DIFdelend with hundreds of other US soldiers as the show \DIFdelbegin \DIFdel{begins}\DIFdelend \DIFaddbegin \DIFadd{began}\DIFaddend , all of them raving maniacally to have the women sign their photos \DIFdelbegin \DIFdel{, }\DIFdelend \DIFaddbegin \DIFadd{and }\DIFaddend touch them. They eventually \DIFdelbegin \DIFdel{swarm }\DIFdelend \DIFaddbegin \DIFadd{swarmed }\DIFaddend the stage, forcing the women to leave. As their helicopter \DIFdelbegin \DIFdel{takes }\DIFdelend \DIFaddbegin \DIFadd{took }\DIFaddend off, two soldiers \DIFdelbegin \DIFdel{cling }\DIFdelend \DIFaddbegin \DIFadd{clung }\DIFaddend onto the helicopter rails. Their efforts \DIFdelbegin \DIFdel{are }\DIFdelend \DIFaddbegin \DIFadd{were }\DIFaddend futile, and they eventually \DIFdelbegin \DIFdel{splash }\DIFdelend \DIFaddbegin \DIFadd{splashed }\DIFaddend into the water below.

Although only temporarily sated with that distraction from the war and the mission, the crew \DIFdelbegin \DIFdel{continues }\DIFdelend \DIFaddbegin \DIFadd{continued }\DIFaddend up the river further towards Kurtz. They eventually \DIFdelbegin \DIFdel{reach }\DIFdelend \DIFaddbegin \DIFadd{reached }\DIFaddend a Medevac camp during a torrential downpour. While trying to find the commanding officer of the camp, Willard \DIFdelbegin \DIFdel{stumbles upon the "agent" }\DIFdelend \DIFaddbegin \DIFadd{stumbled upon the pimp }\DIFaddend of the Playboy models from the show, and \DIFdelbegin \DIFdel{strikes }\DIFdelend \DIFaddbegin \DIFadd{struck }\DIFaddend a deal for his crew to spend time with the women. While Chef and Lance \DIFdelbegin \DIFdel{spend }\DIFdelend \DIFaddbegin \DIFadd{spent }\DIFaddend time with two of the bunnies, it \DIFdelbegin \DIFdel{becomes }\DIFdelend \DIFaddbegin \DIFadd{became }\DIFaddend apparent the bunnies are not entirely willing to be there. Lance \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend told by the woman he \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend spending time with, the Playmate of the Year, she \DIFdelbegin \DIFdel{has }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend done things that she was very against because it \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend almost a survival instinct. Chef \DIFdelbegin \DIFdel{ignores }\DIFdelend \DIFaddbegin \DIFadd{ignored }\DIFaddend the woman he \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend with, Miss May. As she \DIFdelbegin \DIFdel{talks }\DIFdelend \DIFaddbegin \DIFadd{talked }\DIFaddend about her love for birds, Chef \DIFdelbegin \DIFdel{undresses and poses }\DIFdelend \DIFaddbegin \DIFadd{undressed and posed }\DIFaddend her to be a mirror of his favorite picture of her from the Playboy calendar. Eventually, he \DIFdelbegin \DIFdel{begins }\DIFdelend \DIFaddbegin \DIFadd{began }\DIFaddend to act like a bird, causing her to become sexually aroused and leading to them having sex. After leaving the Medevac camp, Clean \DIFdelbegin \DIFdel{complains }\DIFdelend \DIFaddbegin \DIFadd{complained }\DIFaddend about not being able to spend time with either bunny, \DIFdelbegin \DIFdel{and gets }\DIFdelend \DIFaddbegin \DIFadd{but got }\DIFaddend shrugged off by both Chef and Lance. Chef in particular \DIFdelbegin \DIFdel{makes }\DIFdelend \DIFaddbegin \DIFadd{made }\DIFaddend fun of Clean and how "he still needs to pop his cherry" \DIFdelbegin \DIFdel{. Lance is }\DIFdelend \DIFaddbegin \DIFadd{(Coppola, 1979). Lance was }\DIFaddend very quiet about his \DIFdelbegin \DIFdel{experiences}\DIFdelend \DIFaddbegin \DIFadd{experience}\DIFaddend , and instead \DIFdelbegin \DIFdel{paint }\DIFdelend \DIFaddbegin \DIFadd{painted }\DIFaddend camouflage on his face, saying it will save him from the "Charlies" seeing him \DIFaddbegin \DIFadd{(Coppola, 1979)}\DIFaddend .

Further down the river, they \DIFdelbegin \DIFdel{stop }\DIFdelend \DIFaddbegin \DIFadd{stopped }\DIFaddend a trading boat for a routine \DIFdelbegin \DIFdel{check for weapons or }\DIFdelend \DIFaddbegin \DIFadd{weapons check for }\DIFaddend Vietcong support. Willard \DIFdelbegin \DIFdel{demands }\DIFdelend \DIFaddbegin \DIFadd{demanded }\DIFaddend they do not \DIFaddbegin \DIFadd{perform the check}\DIFaddend , but Chief \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend insistent, telling Willard they have more than just the orders from Willard to follow. Chef \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend ordered to check the boat, but \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend extremely resilient. Eventually he does, throwing anything he \DIFdelbegin \DIFdel{finds }\DIFdelend \DIFaddbegin \DIFadd{found }\DIFaddend around in a rage. Nothing \DIFdelbegin \DIFdel{shows }\DIFdelend \DIFaddbegin \DIFadd{showed }\DIFaddend up until a yellow barrel set everyone off guard, \DIFdelbegin \DIFdel{causing }\DIFdelend \DIFaddbegin \DIFadd{which caused }\DIFaddend a Vietnamese woman to frantically yell not to check it. Clean then \DIFdelbegin \DIFdel{loses }\DIFdelend \DIFaddbegin \DIFadd{lost }\DIFaddend it, and \DIFdelbegin \DIFdel{begins }\DIFdelend \DIFaddbegin \DIFadd{began }\DIFaddend firing the machine gun at the trade boat, leading Lance to fire maniacally as well, killing all but the Vietnamese woman. After the chaotic gunfire, all they \DIFdelbegin \DIFdel{find is }\DIFdelend \DIFaddbegin \DIFadd{found was }\DIFaddend a puppy, which Lance \DIFdelbegin \DIFdel{takes }\DIFdelend \DIFaddbegin \DIFadd{took }\DIFaddend as his own. While Chief \DIFdelbegin \DIFdel{tells }\DIFdelend \DIFaddbegin \DIFadd{told }\DIFaddend Chef to bring the woman \DIFdelbegin \DIFdel{over to bring }\DIFdelend to a hospital, Willard \DIFdelbegin \DIFdel{kills }\DIFdelend \DIFaddbegin \DIFadd{killed }\DIFaddend her, reinforcing his previous statement to not stop.

All crew \DIFdelbegin \DIFdel{are }\DIFdelend \DIFaddbegin \DIFadd{were }\DIFaddend silent moving on, until they \DIFdelbegin \DIFdel{arrive }\DIFdelend \DIFaddbegin \DIFadd{arrived }\DIFaddend at the last US station, the Do Long Bridge, a bridge constantly being destroyed at night and rebuilt in the day. Willard and Lance \DIFdelbegin \DIFdel{begin }\DIFdelend \DIFaddbegin \DIFadd{began }\DIFaddend the search for the commanding officer, slowly realizing the insanity and chaos the men at the bridge have fallen\DIFdelbegin \DIFdel{into}\DIFdelend . Watching the bridge slowly collapse from Vietcong fire, they \DIFdelbegin \DIFdel{leave }\DIFdelend \DIFaddbegin \DIFadd{left }\DIFaddend with no fuel or assistance, and \DIFdelbegin \DIFdel{continue }\DIFdelend \DIFaddbegin \DIFadd{continued }\DIFaddend the increasingly chaotic path down to Kurtz. Shortly after passing through the Do Long Bridge, Willard \DIFdelbegin \DIFdel{learns }\DIFdelend \DIFaddbegin \DIFadd{learned }\DIFaddend the old commanding officer, Captain Colby, had been sent on the same mission he is on, but was converted into Kurtz's colony.

Out of nowhere, a barrage of fire \DIFdelbegin \DIFdel{consumes }\DIFdelend \DIFaddbegin \DIFadd{consumed }\DIFaddend the boat, \DIFdelbegin \DIFdel{cause panic and return }\DIFdelend \DIFaddbegin \DIFadd{causing panic and returned }\DIFaddend fire. In the heat of the firefight, Clean is downed, and only \DIFdelbegin \DIFdel{after does }\DIFdelend \DIFaddbegin \DIFadd{afterwards did }\DIFaddend the rest of the crew realize he is dead. 
The combination of all previous stressors from the war and the recent death of Clean \DIFdelbegin \DIFdel{drive }\DIFdelend \DIFaddbegin \DIFadd{drove }\DIFaddend Lance and Chef to excessive drug use. Devastated by the death of their 17 year old comrade, the sullen crew is stopped in the fog by \DIFdelbegin \DIFdel{a mysterious by }\DIFdelend \DIFaddbegin \DIFadd{mysterious }\DIFaddend French troops. After speaking with them, they \DIFdelbegin \DIFdel{come }\DIFdelend \DIFaddbegin \DIFadd{came }\DIFaddend to an agreement, letting the US soldiers bury and respectfully say goodbye to Clean. Afterwards, Willard \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend invited to a dinner, where he \DIFdelbegin \DIFdel{learns }\DIFdelend \DIFaddbegin \DIFadd{learned }\DIFaddend about the French clan's plantation and how determined they \DIFdelbegin \DIFdel{are }\DIFdelend \DIFaddbegin \DIFadd{were }\DIFaddend to stay. After losing World War \DIFdelbegin \DIFdel{1 and 2, these French demand }\DIFdelend \DIFaddbegin \DIFadd{I and II, the French demanded }\DIFaddend victory even to death. When Willard \DIFdelbegin \DIFdel{becomes }\DIFdelend \DIFaddbegin \DIFadd{became }\DIFaddend befuddled and confused why they would be so committed, the French \DIFdelbegin \DIFdel{become }\DIFdelend \DIFaddbegin \DIFadd{became }\DIFaddend enraged with Willard and the US Army in general. They \DIFdelbegin \DIFdel{point }\DIFdelend \DIFaddbegin \DIFadd{pointed }\DIFaddend out the US may \DIFdelbegin \DIFdel{win }\DIFdelend \DIFaddbegin \DIFadd{have won }\DIFaddend every battle, but \DIFdelbegin \DIFdel{have }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend no chance to win the war. Nothing \DIFdelbegin \DIFdel{can be gained here }\DIFdelend \DIFaddbegin \DIFadd{could be gained there }\DIFaddend for the US. This \DIFdelbegin \DIFdel{drives }\DIFdelend \DIFaddbegin \DIFadd{powerful statement drove }\DIFaddend everyone else to retire for the evening.

One particular women, Roxanne, \DIFdelbegin \DIFdel{stays, and begins }\DIFdelend \DIFaddbegin \DIFadd{stayed, and began }\DIFaddend connecting with Willard. Roxanne lost her husband, and \DIFdelbegin \DIFdel{tells }\DIFdelend \DIFaddbegin \DIFadd{told }\DIFaddend Willard about how she would tell him "There are two of you don't you see? One that kills. One that loves." \DIFdelbegin \DIFdel{Willard begins }\DIFdelend \DIFaddbegin \DIFadd{(Coppola, 1979). Willard began }\DIFaddend to realize he is exactly that, a man that \DIFdelbegin \DIFdel{kills}\DIFdelend \DIFaddbegin \DIFadd{killed}\DIFaddend , and a man that \DIFdelbegin \DIFdel{loves. However}\DIFdelend \DIFaddbegin \DIFadd{loved. However, }\DIFaddend his love had been lost when he left his home and his family, becoming enthralled in the war. Only during his time with Roxanne \DIFdelbegin \DIFdel{does }\DIFdelend \DIFaddbegin \DIFadd{did }\DIFaddend he briefly remember his love.

On the final stretch to Kurtz, Chief and Willard \DIFdelbegin \DIFdel{flare }\DIFdelend \DIFaddbegin \DIFadd{flared }\DIFaddend up at each other, arguing over whether the mission \DIFdelbegin \DIFdel{has }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend been worth the losses. \DIFdelbegin \DIFdel{Another barrage floods the boatagain, except this time of arrows. Chief orders return fire, but after Willard realizes }\DIFdelend \DIFaddbegin \DIFadd{A barrage of arrows flooded the boat, and Chief ordered return fire. After Willard realized }\DIFaddend they are just toy arrows, he \DIFdelbegin \DIFdel{demands }\DIFdelend \DIFaddbegin \DIFadd{demanded }\DIFaddend a cease fire. Chief \DIFdelbegin \DIFdel{becomes }\DIFdelend \DIFaddbegin \DIFadd{became }\DIFaddend further enraged with Willard's desire for power. As he \DIFdelbegin \DIFdel{spews }\DIFdelend \DIFaddbegin \DIFadd{spewed }\DIFaddend slanders towards Willard, a spear \DIFdelbegin \DIFdel{impales }\DIFdelend \DIFaddbegin \DIFadd{impaled }\DIFaddend him. Coughing up his own blood, he \DIFdelbegin \DIFdel{attempts }\DIFdelend \DIFaddbegin \DIFadd{attempted }\DIFaddend to choke out Willard, a last effort to save his remaining crew, but Willard \DIFdelbegin \DIFdel{responds and smothers }\DIFdelend \DIFaddbegin \DIFadd{responded and smothered }\DIFaddend Chief.

Having lost two men, the remaining crew, Chef, Lance, and Willard, finally \DIFdelbegin \DIFdel{arrive }\DIFdelend \DIFaddbegin \DIFadd{arrived }\DIFaddend at Kurtz's base. They are greeted by a single American photographer and hundreds of Kurtz's followers. The photographer \DIFdelbegin \DIFdel{guides }\DIFdelend \DIFaddbegin \DIFadd{guided }\DIFaddend Willard and Lance through the colony \DIFdelbegin \DIFdel{, Chef staying on the boat, and continually praises }\DIFdelend \DIFaddbegin \DIFadd{and continually praised }\DIFaddend Kurtz as a god. The two slowly \DIFdelbegin \DIFdel{realize }\DIFdelend \DIFaddbegin \DIFadd{realized }\DIFaddend the severity of madness that Kurtz \DIFdelbegin \DIFdel{has }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend descended into, ruthlessly murdering anyone who \DIFdelbegin \DIFdel{defies }\DIFdelend \DIFaddbegin \DIFadd{defied }\DIFaddend his reign and mutilating the bodies of fallen enemies. While exploring the camp, they \DIFdelbegin \DIFdel{come }\DIFdelend \DIFaddbegin \DIFadd{came }\DIFaddend across the practically brainwashed Colby, the ex-commanding officer of the \DIFdelbegin \DIFdel{DO }\DIFdelend \DIFaddbegin \DIFadd{Do }\DIFaddend Long Bridge and last man sent to assassinate Kurtz. As the new servant \DIFdelbegin \DIFdel{stares }\DIFdelend \DIFaddbegin \DIFadd{stared }\DIFaddend down Willard and Chef, they \DIFdelbegin \DIFdel{realize }\DIFdelend \DIFaddbegin \DIFadd{realized }\DIFaddend the extreme devotion these people \DIFdelbegin \DIFdel{have }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend for Kurtz.

\DIFdelbegin \DIFdel{They return from the boat again, this time }\DIFdelend Willard and Lance \DIFdelbegin \DIFdel{, }\DIFdelend \DIFaddbegin \DIFadd{returned to the village }\DIFaddend to talk to Kurtz, telling Chef to call an airstrike if they \DIFdelbegin \DIFdel{do not return}\DIFdelend \DIFaddbegin \DIFadd{did not come back}\DIFaddend . While finally meeting Kurtz in person, Willard is captured and imprisoned, while Lance, having totally lost touch with himself and reality, \DIFdelbegin \DIFdel{becomes }\DIFdelend \DIFaddbegin \DIFadd{became }\DIFaddend one of Kurtz's men. Willard, now beaten and tied to a pole, \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend visited by Kurtz, who \DIFdelbegin \DIFdel{drops }\DIFdelend \DIFaddbegin \DIFadd{dropped }\DIFaddend the head of Chef on his lap. Willard \DIFdelbegin \DIFdel{realizes }\DIFdelend \DIFaddbegin \DIFadd{realized }\DIFaddend Chef had not gotten the air strike called in and \DIFdelbegin \DIFdel{becomes }\DIFdelend \DIFaddbegin \DIFadd{became }\DIFaddend distraught, crying out for the mistakes he \DIFdelbegin \DIFdel{has }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend made.

Eventually he \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend set free, under prohibition, wandering the colony Kurtz \DIFdelbegin \DIFdel{has }\DIFdelend built. While under watch, Kurtz \DIFdelbegin \DIFdel{lectures }\DIFdelend \DIFaddbegin \DIFadd{lectured }\DIFaddend Willard on the reality of war and humanity, reflecting the French plantation words that US \DIFdelbegin \DIFdel{can }\DIFdelend \DIFaddbegin \DIFadd{could }\DIFaddend not win with the dedication of the Vietcong.

That night the colony \DIFdelbegin \DIFdel{throws }\DIFdelend \DIFaddbegin \DIFadd{threw }\DIFaddend a celebration, so Willard \DIFdelbegin \DIFdel{takes }\DIFdelend \DIFaddbegin \DIFadd{took }\DIFaddend the opportunity to sneak into Kurtz quarters. As Kurtz \DIFdelbegin \DIFdel{reads }\DIFdelend \DIFaddbegin \DIFadd{read }\DIFaddend off quotes to be sent to the US army, Willard \DIFdelbegin \DIFdel{attacks }\DIFdelend \DIFaddbegin \DIFadd{attacked }\DIFaddend him with a machete, eventually forcing Kurtz to the ground. As Kurtz \DIFdelbegin \DIFdel{breaths }\DIFdelend \DIFaddbegin \DIFadd{breathes }\DIFaddend his final breaths, he \DIFdelbegin \DIFdel{utters }\DIFdelend \DIFaddbegin \DIFadd{uttered }\DIFaddend the words "The horror...the horror..." \DIFaddbegin \DIFadd{(Coppola, 1979)}\DIFaddend . As Willard \DIFdelbegin \DIFdel{leaves }\DIFdelend \DIFaddbegin \DIFadd{left }\DIFaddend from Kurtz's quarters, praised by the \DIFdelbegin \DIFdel{now aware colonyas the new god}\DIFdelend \DIFaddbegin \DIFadd{colony, who were aware Kurtz had been killed}\DIFaddend , he grabs Lance to leave. The film \DIFdelbegin \DIFdel{finishes }\DIFdelend \DIFaddbegin \DIFadd{finished }\DIFaddend with the two leaving the colony  in silence, begging the question of who is really insane in war, particularly when it can not be won.

\section{Applications to Abnormal Psychology}

The film \DIFdelbegin \DIFdel{portrays }\DIFdelend \DIFaddbegin \DIFadd{portrayed }\DIFaddend the psychological effects \DIFdelbegin \DIFdel{have }\DIFdelend \DIFaddbegin \DIFadd{war had }\DIFaddend on many characters, prominently Willard, Chef, and Lance.

Willard \DIFdelbegin \DIFdel{exhibits }\DIFdelend \DIFaddbegin \DIFadd{exhibited }\DIFaddend many symptoms throughout the film, many of which fall under the diagnosis of \DIFdelbegin \DIFdel{Post-Traumatic Stress Disorder . Using the DSM-V, the following symptoms can be evaluated as such }\DIFdelend \DIFaddbegin \DIFadd{Posttraumatic Stress Disorder (PTSD). The following symptoms of PTSD are exhibited by Willard }\DIFaddend (American Psychiatric Association, 2013):
\begin{itemize}
\item Previous Vietnam tour, indicative of potential exposure to death or major injury.
\item Vivid dream of previous combat, or repeated, intrusive exposure.
\item Divorce after returning to the US, having said "The only words I spoke to my wife were 'Yes' when she asked for a divorce", showing both little interest in important events and feelings of detachment \DIFaddbegin \DIFadd{(Coppola, 1979)}\DIFaddend .
\item Excessive drinking, smoking, punching a mirror, and other self harm \DIFaddbegin \DIFadd{acts}\DIFaddend , exhibiting irritable\DIFdelbegin \DIFdel{and reckless, }\DIFdelend \DIFaddbegin \DIFadd{, reckless, and }\DIFaddend self-harming behaviors.
\item Has been a changed person since the previous tour, over \DIFdelbegin \DIFdel{1 }\DIFdelend \DIFaddbegin \DIFadd{one }\DIFaddend month ago.
\end{itemize} 
Willard appears to be another not uncommon case of a soldier returning from war with PTSD\DIFdelbegin \DIFdel{, howeverthere a }\DIFdelend \DIFaddbegin \DIFadd{; however, there are }\DIFaddend few missing criteria from the DSM-V that Willard \DIFdelbegin \DIFdel{fails }\DIFdelend \DIFaddbegin \DIFadd{failed }\DIFaddend to show, or are the opposite of symptoms for the diagnosis (American Psychiatric Association, 2013):
\begin{itemize}
\item Willard desires to be back "in the jungle", or back on a mission, which would counter that the original trauma was during his first tour \DIFaddbegin \DIFadd{(Coppola, 1979)}\DIFaddend .
\item Willard has no exaggerated or distorted memories of the previous tour.
\item Willard wants to return, which shows a lack of avoidance behaviors.
\item Willard experiences happiness, as well as interacting with the crew well.
\end{itemize}
The first three points would prevent a diagnosis of PTSD for Willard, while the last would not necessarily effect the diagnosis either way, since it is part of a subset of symptoms that Willard \DIFdelbegin \DIFdel{exhibits }\DIFdelend \DIFaddbegin \DIFadd{exhibited }\DIFaddend (American Psychiatric Association, 2013). His obsession with returning to the jungle could \DIFdelbegin \DIFdel{be though as part of Obsessive-Compulsive Disorder, however the obsession is }\DIFdelend \DIFaddbegin \DIFadd{exhibit symptoms of Obsessive Compulsive Disorder, but the obsession was }\DIFaddend not unwanted, not causing stress, and there \DIFdelbegin \DIFdel{are }\DIFdelend \DIFaddbegin \DIFadd{were }\DIFaddend no cleansing compulsions to reduce or get rid of the obsession (American Psychiatric Association, 2013).

Chef \DIFdelbegin \DIFdel{seems }\DIFdelend \DIFaddbegin \DIFadd{seemed }\DIFaddend a rather normal man by military standards, interacting with his crew, coping with the situations he \DIFdelbegin \DIFdel{has }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend faced rather well. However, the hellish mission he \DIFdelbegin \DIFdel{embarks }\DIFdelend \DIFaddbegin \DIFadd{embarked }\DIFaddend on with Willard \DIFdelbegin \DIFdel{causes this }\DIFdelend \DIFaddbegin \DIFadd{caused his mental state }\DIFaddend to change. As they \DIFdelbegin \DIFdel{continue }\DIFdelend \DIFaddbegin \DIFadd{continued }\DIFaddend further up the Nung River, Chef \DIFdelbegin \DIFdel{begins }\DIFdelend \DIFaddbegin \DIFadd{began }\DIFaddend to develop symptoms of Acute Stress Disorder as follows (American Psychiatric Association, 2013):
\begin{itemize}
\item Chef is attacked by a tiger, having a near death experience. He also witnesses the death of 17 year old Clean, another traumatic event.
\item While searching the boat, he is extremely resistance to begin the search and becomes enraged while searching, showing avoidance and arousal symptoms
\item Chef consistently disagrees with Willard's mission, and questions why they are helping him anyways, exhibiting persistent negative behavior
\end{itemize}
Although he also \DIFdelbegin \DIFdel{has }\DIFdelend \DIFaddbegin \DIFadd{had }\DIFaddend symptoms of a \DIFdelbegin \DIFdel{substance abuse disorder}\DIFdelend \DIFaddbegin \DIFadd{Substance Use Disorder}\DIFaddend , specifically when he and Lance \DIFdelbegin \DIFdel{start excessive }\DIFdelend \DIFaddbegin \DIFadd{started excessive drug }\DIFaddend use after Clean's death, this \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend a response to the stress, and thus would not be Substance Use Disorder, \DIFaddbegin \DIFadd{but }\DIFaddend rather Acute Stress Disorder with a response of substance use. \DIFdelbegin \DIFdel{However, }\DIFdelend \DIFaddbegin \DIFadd{But }\DIFaddend even with these \DIFaddbegin \DIFadd{symptoms }\DIFaddend present, there \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend a definitive lack of \DIFdelbegin \DIFdel{and }\DIFdelend \DIFaddbegin \DIFadd{any }\DIFaddend dissociative symptoms. He also \DIFdelbegin \DIFdel{exhibits }\DIFdelend \DIFaddbegin \DIFadd{exhibited }\DIFaddend no intrusion symptoms since no flashbacks are present, and the intense and prolonged stress \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend not caused from the traumatic events specifically, but \DIFdelbegin \DIFdel{are }\DIFdelend \DIFaddbegin \DIFadd{were }\DIFaddend rather the stressful events in the moment (American Psychiatric Association, 2013). 

Lance \DIFdelbegin \DIFdel{begins }\DIFdelend \DIFaddbegin \DIFadd{began }\DIFaddend the film a very naive, California surfer, almost out of place in the Vietnam War. As more \DIFdelbegin \DIFdel{and more }\DIFdelend significantly stressful events \DIFdelbegin \DIFdel{occur, he relapses }\DIFdelend \DIFaddbegin \DIFadd{occurred, he relapsed }\DIFaddend into a shell, showing signs of Major Depressive Disorder (American Psychiatric Association, 2013):
\begin{itemize}
\item Lance shows significant physical lethargy, or psychomotor retardation.
\item Lance does not take interest in many activities, even ones outside the mission
\item Along with the lethargy, Lance appears exhausted even when rested outside the stressful combat and other events
\item Lance does not appear comfortable in any situation outside his times with the puppy
\item There is no known excessive substance use to cause the distress
\end{itemize}
However, there are not enough \DIFdelbegin \DIFdel{shown }\DIFdelend symptoms to diagnose Lance with Major Depressive Disorder. Instead, he might \DIFdelbegin \DIFdel{be experiencing Depressive }\DIFdelend \DIFaddbegin \DIFadd{have experienced a depressive }\DIFaddend episode with insufficient symptoms. This \DIFdelbegin \DIFdel{would be a more accurate diagnosis with the known symptoms }\DIFdelend \DIFaddbegin \DIFadd{diagnosis would be more accurate given the symptoms exhibited }\DIFaddend in the film, as well as the lack of any manic episodes or other bipolar specific symptoms (American Psychiatric Association, 2013). He could also be diagnosed with PTSD, using the death of Clean and Chief as the trauma. Similarly to Chef, he could be diagnosed with a substance use response, since the substance use only appeared after the original symptoms for depression or PTSD.

\section{Conclusion}	

According to the DSM-V, Willard \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{was }\DIFaddend the only person who \DIFdelbegin \DIFdel{could get diagnosed with a disorder, in his case }\DIFdelend \DIFaddbegin \DIFadd{met the diagnosis for }\DIFaddend PTSD. Chef could \DIFdelbegin \DIFdel{possibly have }\DIFdelend \DIFaddbegin \DIFadd{have possibly had }\DIFaddend more symptoms, however\DIFdelbegin \DIFdel{the film does }\DIFdelend \DIFaddbegin \DIFadd{, the film did }\DIFaddend not portray them. Further, he could have an Unspecified \DIFdelbegin \DIFdel{Trauma- }\DIFdelend \DIFaddbegin \DIFadd{Trauma }\DIFaddend and Stressor-Related Disorder, since his \DIFdelbegin \DIFdel{symptoms are }\DIFdelend \DIFaddbegin \DIFadd{lack of symptoms were }\DIFaddend not definitive of Acute Stress Disorder or another specific stress disorder. Lance could be diagnosed with Major Depressive Disorder, although it would require more symptoms to \DIFaddbegin \DIFadd{have }\DIFaddend be present. With the films portrayal, it is more likely he \DIFdelbegin \DIFdel{is }\DIFdelend \DIFaddbegin \DIFadd{would be }\DIFaddend diagnosed with a \DIFdelbegin \DIFdel{Depressive }\DIFdelend \DIFaddbegin \DIFadd{depressive }\DIFaddend episode lacking sufficient symptoms or PTSD with catatonic behaviors, since he changed his behaviors after the death of Clean. Lance and Chef could both also have \DIFdelbegin \DIFdel{an Substance Use }\DIFdelend \DIFaddbegin \DIFadd{Substance Use Disorder }\DIFaddend added as a response to their potential diagnosis. \\

\raggedbottom
\pagebreak
\section{References}

\noindent American Psychiatric Association. (2013). Diagnostic and statistical manual of mental
\indent disorders (5th ed.). Washington, DC: Author.

\noindent Coppola, F. F. (Producer), \& Coppola, F. F. (Director). (1979). \textit{Apocalypse Now}
\indent [Motion picture]. United States: Omni Zoetrope Studios.


\end{document}